Results Analysis

### 2024-11-12 analysis/resultsAnalysis.Rmd
Moved via the Open Science Framework

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  html_document: default
---

@@

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(ggplot2)
library(RColorBrewer)
library(assertthat)
```

@@

Count randomly selected journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

@@

randomCategory
```
## How many journals offer post-publication critique?

PROMINENT SAMPLE
Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

promCOPE
```
RANDOMLY-SELECTED SAMPLE
Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

@@

@@

## Calculations for Table 1: PPC limits in prominent journals

Check length limits placed on PPC options in prominent journals
```{r}
# Summarise length statistics for All Types
prominentLengthAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 )

prominentLengthAll
```

``` {r}
# Summarise length Statistics for each PPC type
prominentLengthType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = quantile(quantLength, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantLength, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

prominentLengthType
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
prominentTimeAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 )

prominentTimeAll
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
prominentTimeType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = quantile(quantTime, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantTime, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

prominentTimeType
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
prominentRefAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 )

prominentRefAll
```

```{r}
# Summarise reference statistics by type
prominentRefType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = quantile(quantRef, probs = 0.25, na.rm = TRUE),
    Q3 = quantile(quantRef, probs = 0.75, na.rm = TRUE),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

prominentRefType
```

@@

prominentReviewAll

@@

prominentReviewType
```

## Calculations for Table 2: PPC limits in randomly selected journals

>>>>

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  html_document: default
  pdf_document: default
---

@@

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(assertthat)
library(kableExtra)
library(webshot2)
```

@@

*Supplementary Information I: Descriptive statistics for both journal samples*

randomCategory
```

@@

## How many journals offer post-publication critique?

**RANDOMLY-SELECTED SAMPLE**

Inspect how frequently PPC policies were stated for randomly selected journals 
```{r}
randomPPC <- dj_random %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

@@

**PROMINENT SAMPLE**

Inspect how frequently PPC policies were stated for prominent journals 
```{r}
prominentPPC <- dj_prominent %>%
  filter(ppc_type == 'A') %>%
  group_by(has_ppc) %>%
  summarise(count = n()) %>%
  ungroup()

promCOPE
```

@@

## Calculations for Table 1: PPC limits in randomly selected journals

Check length limits placed on PPC options in randomly selected journals
```{r}
# Summarise length statistics for All Types
randomLengthAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomLengthAll_1 <- randomLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
randomLengthType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = Q3 - Q1 
 ) %>%
  ungroup()

# Put results into desired table format
randomLengthType_1 <- randomLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomLength_combo <- bind_rows(
  randomLengthType_1,
  randomLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
randomTimeAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = Q3 - Q1 
 )

# Put results into desired table format
randomTimeAll_1 <- randomTimeAll %>% 
  mutate('Post-publication critique type' = "All Types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
randomTimeType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = median(quantTime, na.rm = TRUE),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomTimeType_1 <- randomTimeType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all time limits into single table
randomTime_combo <- bind_rows(
  randomTimeType_1,
  randomTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
randomRefAll <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
randomRefAll_1 <- randomRefAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
randomRefType <- dj_random %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
randomRefType_1 <- randomRefType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
randomRef_combo <- bind_rows(
  randomRefType_1,
  randomRefAll_1
)
```

Check how many PPC options are sent for external peer review in prominent journals
```{r}
# Peer review statistics for All Types
randomReviewAll <- dj_random %>%
  select(c(journal_name, ppc_name, ppc_review)) %>%
  filter(!is.na(ppc_name)) %>%
  summarise(anyReview = n() - sum(ppc_review == "NOT STATED"),
            yesReview = anyReview - sum(ppc_review == "NO"),
            yesPercent = round((yesReview / n()) * 100)   # Percentage reviewed from All Types 
  )

# Put results into desired table format
randomReviewAll_1 <- randomReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

# Put results into desired table format
randomReviewType_1 <- randomReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
randomReview_combo <- bind_rows(
  randomReviewType_1,
  randomReviewAll_1
)
```

**Table 1.** Post-publication critique types identified in randomly selected psychology journals and their length, time-to-submit, and reference limits.

``` {r}
# Give each table a separate header for results
randomLengthTable <- randomLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

randomTimeTable <- randomTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

randomRefTable <- randomRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

randomReviewTable <- randomReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))
```

```{r}
# Combine the random sample limitations data frames
combined_df <- bind_cols(
  randomLength_combo %>% select(-`Post-publication critique type`),
  randomTime_combo %>% select(-`Post-publication critique type`),
  randomRef_combo %>% select(-`Post-publication critique type`),
  randomReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(randomLength_combo %>% select(`Post-publication critique type`), combined_df)

# Create the table with kableExtra
randomLimits_Table <- combined_df %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "any n (%)", "quantitative n (%)", "median (IQR)",
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3, "Time limits" = 3, "Reference limits" = 3, "Peer review" = 1))

randomLimits_Table

save_kable(randomLimits_Table, here("analysis/randomLimits_Table.png"))
```

## Calculations for Table 2: PPC limits in prominent journals

Check length limits placed on PPC options in prominent journals
```{r}
# Summarise length statistics for All Types
prominentLengthAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
prominentLengthAll_1 <- prominentLengthAll %>% 
  mutate('Post-publication critique type' = "All types") %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise length Statistics for each PPC type
prominentLengthType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_length)) %>%
 mutate(quantLength = case_when(
    ppc_length == "NOT STATED" | ppc_length == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_length) # create a column that contains only quantitative limits
  )) %>%
 group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_length == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_length == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianLength = median(quantLength, na.rm = TRUE),
    Q1 = round(quantile(quantLength, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantLength, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentLengthType_1 <- prominentLengthType %>% 
  mutate('Post-publication critique type' = ppc_name) %>% 
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>% 
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>% 
  mutate('median (IQR)' = paste(medianLength, " (", Q1, " - ", Q3, ")", sep = "")) %>% 
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentLength_combo <- bind_rows(
  prominentLengthType_1,
  prominentLengthAll_1
)
```

Check time-to-submit limits placed on PPC options in prominent journals
```{r}
# Summarise time-to-submit statistics for All Types
prominentTimeAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1) 
 )

# Put results into desired table format
prominentTimeAll_1 <- prominentTimeAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

``` {r}
# Summarise time-to-submit Statistics for each PPC type
prominentTimeType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_time)) %>%
 mutate(quantTime = case_when(
    ppc_time == "NOT STATED" | ppc_time == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_time) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_time == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_time == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianTime = round(median(quantTime, na.rm = TRUE)),
    Q1 = round(quantile(quantTime, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantTime, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentTimeType_1 <- prominentTimeType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianTime, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentTime_combo <- bind_rows(
  prominentTimeType_1,
  prominentTimeAll_1
)
```

Check reference limits placed on PPC options in prominent journals
```{r}
# Summarise reference statistics for All Types
prominentRefAll <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 )

# Put results into desired table format
prominentRefAll_1 <- prominentRefAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Summarise reference statistics by type
prominentRefType <- dj_prominent %>%
 filter(!is.na(ppc_name)) %>% 
 select(c(journal_name, ppc_name, ppc_ref)) %>%
 mutate(quantRef = case_when(
    ppc_ref == "NOT STATED" | ppc_ref == "Qualitative" ~ NA_real_,
    TRUE ~ as.numeric(ppc_ref) # create a column that contains only quantitative limits
  )) %>%
  group_by(ppc_name) %>%
 summarise(
    anyLimit = n() - sum(ppc_ref == "NOT STATED"),
    anyPercent = round((anyLimit / n()) * 100),
    quantLimit = anyLimit - sum(ppc_ref == "Qualitative"),
    quantPercent = round((quantLimit / n()) * 100),
    medianRef = median(quantRef, na.rm = TRUE),
    Q1 = round(quantile(quantRef, probs = 0.25, na.rm = TRUE)),
    Q3 = round(quantile(quantRef, probs = 0.75, na.rm = TRUE)),
    IQR = round(Q3 - Q1)
 ) %>%
  ungroup()

# Put results into desired table format
prominentRefType_1 <- prominentRefType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('any n (%)' = paste(anyLimit, " (", anyPercent, ")", sep = "")) %>%
  mutate('quantitative n (%)' = paste(quantLimit, " (", quantPercent, ")", sep = "")) %>%
  mutate('median (IQR)' = paste(medianRef, " (", Q1, " - ", Q3, ")", sep = "")) %>%
  select('Post-publication critique type', 'any n (%)', 'quantitative n (%)', 'median (IQR)')
```

```{r}
# Combine all peer review into single table
prominentRef_combo <- bind_rows(
  prominentRefType_1,
  prominentRefAll_1
)
```

@@

# Put results into desired table format
prominentReviewAll_1 <- prominentReviewAll %>%
  mutate('Post-publication critique type' = "All types") %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

# Put results into desired table format
prominentReviewType_1 <- prominentReviewType %>%
  mutate('Post-publication critique type' = ppc_name) %>%
  mutate('YES n (%)' = paste(yesReview, " (", yesPercent, ")", sep = "")) %>%
  select('Post-publication critique type', 'YES n (%)')
```

```{r}
# Combine all peer review into single table
prominentReview_combo <- bind_rows(
  prominentReviewType_1,
  prominentReviewAll_1
)
```

**Table 2.** Post-publication critique types identified in prominent psychology journals and their length, time-to-submit, and reference limits.

``` {r}
# Give each table a separate header for results
prominentLengthTable <- prominentLength_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Length limits" = 3))

prominentTimeTable <- prominentTime_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Time limits" = 3))

prominentRefTable <- prominentRef_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "any n (%)", 
                              "quantitative n (%)", 
                              "median (IQR)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Reference limits" = 3))

prominentReviewTable <- prominentReview_combo %>%
  kable("html", col.names = c("Post-publication critique type", 
                              "YES n (%)")) %>%
  kable_styling(full_width = F) %>%
  add_header_above(c(" " = 1, "Peer review" = 1))

@@

```{r}
# Combine the prominent limitations data frames
combined_df <- bind_cols(
  prominentLength_combo %>% select(-`Post-publication critique type`),
  prominentTime_combo %>% select(-`Post-publication critique type`),
  prominentRef_combo %>% select(-`Post-publication critique type`),
  prominentReview_combo %>% select(-`Post-publication critique type`)
)

# Add the 'Post-publication critique type' column back to the combined data frame
combined_df <- bind_cols(prominentLength_combo %>% select(`Post-publication critique type`), combined_df)
